\documentclass[a4paper,11pt,openright]{report}
\setlength{\parindent}{0pt} % set noindent for entire file

\usepackage[utf8]{inputenc}
\usepackage[a4paper, left=10mm, right=10mm, top=20mm]{geometry}
\usepackage{xcolor,graphicx}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{sectsty}
\usepackage{etoolbox}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{times}
%\usepackage{lmodern}

\graphicspath{ {/home/saran/Analytics/May_01/} }

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{white},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,
	breaklines=true,
	captionpos=b,
	keepspaces=true,
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	tabsize=4
}

\lstset{style=mystyle}

\begin{document}
\singlespacing
\pagestyle{plain}

\begin{center}
\textbf{Assignment Normal Distribution} \\
Date: 04/05/2020 \hspace{2mm} Name: D.Saravanan
\end{center}

\vspace{10px}

\begin{enumerate}

\item[1.] Find the area under the standard normal curve which lie 

\begin{enumerate}

\item[a)] To the right of $Z = 2.70$
\item[b)] To the left of $Z = 1.73$
\item[c)] To the right of $Z = -0.66$
\item[d)] To the left of $Z = -1.88$
\item[e)] Between $Z = -0.90$ and $Z = -1.85$
\item[f)] Between $Z = -1.45$ and $Z = -1.45$
\item[g)] Between $Z = -0.90$ and $Z = 1.58$

\end{enumerate}

\item[2.] The life of a certain kind of electronic device has a mean of $300$ hours and a
standard deviation fo $25$ hours. Assuming that the distribution of life times which are
measured to the nearest hours can be approximated closely with a normal curve.

\begin{enumerate}

\item[a)] Find the probability that any one of these devices will have a lifetime of more
than $350$ hours.
\item[b)] What percentage will have life time from $220$ to $260$ hours?

\end{enumerate}

\item[3.] The customer accounts of a certain departmental store have an average balance of
Rs.$120$ and standard deviation of Rs.$40$ Assuming that the account balances are normally
distributed, find

\begin{enumerate}

\item[a)] What proportion of accounts is over Rs.$150$?
\item[b)] What proportion of accounts is between Rs.$100$ and Rs.$150$?
\item[c)] What proportion of accounts is between Rs.$60$ and Rs.$90$?

\end{enumerate}

\end{enumerate}
\end{document}
